---
title: "Pacific Giant Salamander"
author: "Jennifer Truong & Joanne Pham"
date: "11/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      results = 'hide')
```

```{r}
# Attach packages

library(tidyverse)
library(janitor)
library(here)
library(kableExtra)
library(ggbeeswarm)
library(car)

# Read in Mack Creek Vertebrates.csv

mack_creek_df <- read_csv("mack_creek_vertebrates.csv") %>% 
  clean_names() %>%  # Change column names to lower case
  rename("channeltype" = "unittype") # Rename "unittype" column to "channeltype" for more clarity
```

## Introduction

## Data and Methods

"Old Growth" refers to the 500 year old coniferous forest upstream, while "Clear Cut" refers to the clear-cut section of the forest.

## Results

```{r}
# Data frame to pull for all results. 
mack_creek_data <- mack_creek_df %>% 
  select(entity, section, channeltype, weight, year)

# Note: Weights is in grams (from metadata)
```

### A. Annual Salamander Counts in Old Growth (OG) and Clear Cut (CC) Sections of Mack Creek

```{r}
# Counting for section (clear and old growth)

mack_creek_cc_og <- mack_creek_data %>% 
  count(section, year)

mack_creek_cc_og
```

```{r}
# Graph for changes in yearly salamander population in these two sections over time 

ggplot(data = mack_creek_cc_og, aes(x = year)) +
  geom_histogram(aes(fill = n))
```


### B. Salamander Counts by Channel Classification

### C. Hypothesis Testing: Significant Difference in Location?

### D. Comparison of Salamander Weights in OG and CC Sections

```{r}

```


### E. Comparison of Salamander Weights in Pools, Cascades, and Side Channels

## Summary

## References